### 2022-11-14 NSF2022/Description/backgroundv3.tex
proof reading

Self-organization encompasses a broad range of
interesting and challenging phenomena in engineering and science.
For example, understanding the
organization of lipids and proteins in vesicles is crucial to design
effective drug carriers
and functional mimics of cell membranes
\cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
The COVID-19 pandemic has led to a
concerted, worldwide efforts to understand
the mechanisms of RNA condensation by structural proteins protein
oligomerization that control virus structure
\cite{Kim2021SelfassembledMV}.
Engineers have developed superior techniques
that rely on nanoscale  
capillary and van der Waals forces
to print high-resolution
features on devices \cite{Zeng20223DprintedMT}.
Finally, researchers design efficient algorithms for
constructing for the interaction kernels to study complex
patterns in agent-based systems like swarms and flocking
\cite{Lu2019NonparametricIO,Tadmor2021OnTM}.

@@

When fluids are involved,
tracking self-organization
becomes difficult due to the deformability of
suspended media in the presence of non-local hydrodynamic interactions.  
A dominant approach in this area,
the phase field method
introduce a scalar-valued phase
field function for the volume fraction of
amphiphilic lipids or polymers in solvent, for example.
Sometimes called diffuse interface
methods, one devises energy functionals involving the gradient and
well-potentials of the phase field, and possibly long range interaction
kernels, 
\cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16,Choksi2003OnTD}.
Because the fluid interfaces are given by the
level-set of a smooth function,
they can have almost arbitrary topology
e.g., free ends, junctions
\cite{Promislow2017ExistenceBA,Promislow2022UndulatedBI},
the evolution equations can be studied
by well-established tools variational and analytical means,
\cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
Dai2022GeometricEO,Dai2020MinimizersFT,Dai2013GeometricEO},
and the governing equations are amenable to numerical approximation
\cite{Christlieb2020BenchmarkCO,Christlieb2019CompetitionAC}.
One of the downsides, though, 
is that granular details like molecular orientations and
shape changes induced by proteins that may be crucial to the physics, are
clumsy to incorporate in the model. Moreover, numerical simulations of
phase field models typically discretize the entire fluid domain under
consideration, and apply cutoff boundary conditions when periodic
domains are not under consideration.

@@

The framework is robust, flexible, and
cuts across many of the aforementioned challenges.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull granules apart as physically required.
(ii) The model formulation is built around important details like molecular orientations,
and exhibits inter-molecular slip that must be added into diffusive interface models
post hoc. 
(iii) It is straightforward to consider mixtures of granules with different
types of shapes and boundary conditions.
Leveraging boundary integral and fast summation methods, the dynamics can be solved in 
near-linear complexity in the number of granules,
which is equal to or better than 
the computational complexity of related sharp interface methods.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize
  (a) Granules make a superstructure e.g., a vesicle. The panel shows
  the moving domain $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$,
  and the unit inward normal $\nu.$ Panels b, c, d show the
  interplay between the phase field $\phi$ (colormap) and granule configuration.
  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) = \tfrac{1}{2}\phi^2$.
  The white arrows are the fluid velocity field.  
  }
\end{figure}

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$.

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of
the incompressible fluid region with viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$  etc.
representing metastable states of the solvent.
For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specificaim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition results in a bilayer pattern (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

For the moving domain boundary conditions, equations~\eqref{eqn:noslip}
specify a no-slip boundary condition for a rigid body with translation
velocity $\aa'_i(t) = \vv_i$ and angular velocity $\omega_i$ (the axial
vector for $R'_i(t)R_i(t)^T$) about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at water-granule interface. Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances that
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension, $I$ is the identity matrix,
and we define the ``cross product'' $\aa \times \bb = (\aa^{\perp} \cdot
\bb) \kk$ where $\kk = (0,0,1) \in \RR^3$ and $(a_1,a_2)^{\perp} =
(-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study flow patterns 
arrising from the interaction
between membrane elasticity and the fluid.

\begin{wrapfigure}[11]{l}{0.48\textwidth}
\vspace{-5pt}
\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic
simulations is their fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to their realistic values 
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we quantitatively recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.
\newpage

\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}
In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of an continous, inextensible, elastic vesicle
with permeability. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction were in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that overlapped.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
is highly desirable from the applied math point of view as there are many
\emph{Further Applications}, such as
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[15]{r}{2.1in}
  \vspace{-0pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=2in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs.
\S~\ref{sec:specificaim2} discusses
a variety of tools the IE community,
including PI Quaife, has developed
to address these numerical challenges.

>>>>

The field of self-organization encompasses a broad range of
interesting and challenging phenomena in engineering and science.
For example, understanding the
organization of lipids and proteins in vesicles is crucial to
designing effective drug carriers
and functional mimics of cells
\cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
The COVID-19 pandemic has led to a
concerted effort to understand
the mechanisms of RNA condensation by structural proteins
that control virus structure
\cite{Kim2021SelfassembledMV}.
Engineers have developed superior techniques
that rely on nanoscale  
capillary and van der Waals forces
to print high-resolution
features on devices \cite{Zeng20223DprintedMT}.
Finally, researchers design efficient algorithms for
constructing interaction kernels in the to study 
of agent-based systems like swarms and flocking
\cite{Lu2019NonparametricIO,Tadmor2021OnTM}.

@@

When fluids are involved,
tracking self-organization
becomes difficult due to the deformability of
suspended media in the presence of non-local hydrodynamic interactions.  
The phase field method,
a prominent approach in this area,
introduce a scalar-valued phase
field function for the volume fraction of
amphiphilic lipids or polymers in solvent, for example.
Sometimes called the diffuse interface
method, one devises energy functionals involving the gradient and
well-potentials of the phase field, and possibly convolution
kernels, to characterize the self- and solvent-interaction of the
suspended media 
\cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16,Choksi2003OnTD}.
Because the fluid interfaces are given by 
level-sets of a smooth function,
they can have almost arbitrary topology
e.g., free ends, junctions
\cite{Promislow2017ExistenceBA,Promislow2022UndulatedBI},
the evolution equations can be studied
by well-established variational and analytical tools,
\cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
Dai2022GeometricEO,Dai2020MinimizersFT,Dai2013GeometricEO},
and the governing equations are amenable to numerical approximation
\cite{Christlieb2020BenchmarkCO,Christlieb2019CompetitionAC}.
One of the downsides, though, 
is that granular details like molecular heterogeneity
and orientations that may be crucial to the physics at mesoscopic scales, are
clumsy to incorporate in the model. Moreover,
numerical simulations of
phase field models typically discretize the entire fluid domain, a
nd apply cutoff boundary conditions when periodic
domains are not under consideration.

@@

The framework is robust, flexible, and
cuts across many of the aforementioned challenges.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull groups of granules apart as physically required.
(ii) The model formulation is built around important details like molecular orientations,
and exhibits inter-molecular slip that must be added into diffusive interface models
post hoc. 
(iii) It is straightforward to consider mixtures of granules with different
shapes and boundary conditions.
Leveraging boundary integral and fast summation methods, the dynamics can be solved in 
near-linear complexity in the number of granules,
which is equal to or better than 
the computational complexity of related sharp interface methods.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize
  (a) Granules make a superstructure e.g., a vesicle. The panel shows
  the moving domain $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$,
  and the unit inward normal $\nu.$ Panels b, c, d show the
  interplay between the phase field $\phi$ (colormap) and granule configuration.
  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) = \tfrac{1}{2}\phi^2$.
  The white arrows are the fluid velocity field.
  The panels reach an equilibrium state in panel d.
  }
\end{figure}

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to
the unit normal pointing into $\Omega(t)$.

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of
the incompressible fluid region with viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$,  etc.,
representing metastable states of the solvent.
In the single-well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
In the double-well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specificaim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

For the moving domain, equations~\eqref{eqn:noslip}
specify a no-slip boundary condition for a rigid body with translation
velocity $\aa'_i(t) = \vv_i$ and angular velocity $\omega_i$ (the axial
vector for $R'_i(t)R_i(t)^T$) about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at the solvent-granule interface. Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances
the force and torque 
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension, $I$ is the identity matrix,
and we interpret the ``cross product'' as $\aa \times \bb = (\aa^{\perp} \cdot
\bb) \kk$ where $\kk = (0,0,1) \in \RR^3$ and $(a_1,a_2)^{\perp} =
(-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label
(\S\ref{sec:specificaim1}, equation \eqref{eq:amphiphilic_BC})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study flow patterns 
arrising from the interaction
between membrane elasticity and the fluid.

\begin{wrapfigure}[10]{l}{0.48\textwidth}
\vspace{-5pt}
\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic
simulations is their fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When these are set to realistic values 
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we quantitatively recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
correctly capture the

\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}
\noindent long-range interactions between amphiphilic
granules (such as lipid macromolecules) surfaces.

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continous, permeable, inextensible,
elastic vesicle.
The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction are in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that basically overlapped.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
is highly desirable from the applied math point of view as there are many
\emph{Further Applications}, such as
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension driven fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[18]{r}{3.1in}
  \vspace{-0pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far-field
conditions. Additional advantages of discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs.
\S~\ref{sec:specificaim2} discusses
a variety of tools the IE community,
including PI Quaife, has developed
to address these numerical challenges.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
%\begin{align}
%\label{eq:energy_law}
%  \begin{split}
%  \frac{d}{dt}E
%    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx, \\
%    E &= \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%  \end{split}
%\end{align}
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by the phase transitions
between the granule boundaries and the solvent and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
In terms of self-consistency, the sum of the forces given by the
integral of the phase stress vectors $T_i\nu$ over the granule boundaries
is zero. 
Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the
self-assembly process to
the collective dynamics of the assembly under external forcing.

\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-30pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
\end{wrapfigure}
